Reionization Planck 2018 Notes

### 2020-07-06 results/notes.tex

@@

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde_double_checked_python.png}
\caption{DEBUGGING - updated the python curves with the same covariance matrix, chains, etc (also confirmed that tanh dz = 0.5). 
}
\label{fig:}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde_with_grid_test.png}
\caption{DEBUGGING - tanh dz = 0.5 for all curves. ...)
}
\label{fig:}
\end{figure}
